\section{References}
\begin{enumerate}
  \item Jean-Paul Davis and Bradford Sturtevant , \emph{Separation length in high-enthalpy shock/boundary-layer interaction"}, Physics of Fluids 12, 2661-2687 (2000) https://doi.org/10.1063/1.1289553 
  \item Das D, Desai S, Kulkarni V. \emph{Comparative studies of shock-wave boundary-layer interactions in Earth and Mars atmospheres} . Proceedings of the Institution of Mechanical Engineers, Part G: Journal of Aerospace Engineering. 2022;236(2):324-340. doi:10.1177/09544100211011829
  \item MacLean, M., Holden, M., and Dufrene, A., \emph{Comparison between CFD and Measurements for Real-Gas Effects on Laminar Shock Wave Boundary Layer Interaction, I}, Oral Presentation, AIAA Aviation 2014, Atlanta, GA, 2014
  \item Doyle Knight and Mahsa Mortazavi, \emph{Simulation of Non-equilibrium Hypersonic Shock Wave Boundary
    Layer Interactions Using the Navier-Stokes Equations}, Center for Computational Design
    Dept Mechanical and Aerospace Engineering, Rutgers University, 2018
     \item Menter, F. R. (1994), \emph{Two-Equation Eddy-Viscosity Turbulence Models for Engineering Applications}, AIAA Journal, vol. 32, no 8. pp. 1598-1605., “A New Flux Splitting Scheme,” 
       \item Liou, M.-S. and Steffen, C., \emph{A New Flux Splitting Scheme,},J. Comput. Phys., Vol. 107, 23-39, 1993.
            \item Gnoffo, P, \emph{CFD Validation Studies for Hypersonic Flow Prediction},AIAA Paper 2001-1025, American Institute of Aeronautics and Astronautics, January 2001.
 \item Viren Menezes, S. Saravanan, G. Jagadeesh and K. P. J. Reddy \emph{Experimental Investigations of Hypersonic Flow
over Highly Blunted Cones with Aerospikes},Vol. 41, No. 10, AIAA JOURNAL, American Institute of Aeronautics and Astronautics, October 2003.
            
\end{enumerate}